On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages\\ \large{Not For Distribution}

### 2020-07-30 paper/paper.tex
wibble

\begin{lstlisting}
isEven' :: E Int -> E (Int -> Bool)
isEven' x =
  TailRec ( DoneExp (
    IfThenElseExp (Equal x (rep 0))
      TrueExp
      (IfThenElseExp (Equal x (rep 1))
        FalseExp
        (IsEven' (Sub x (rep 2))))
\end{lstlisting}

>>>>

\begin{lstlisting}
isEven' :: E Int -> E (Int -> Bool)
isEven' x =
  TailRec ( DoneExp (
    IfThenElseExp (Equal x (rep 0))
      TrueExp
      (IfThenElseExp (Equal x (rep 1))
        FalseExp
        (isEven' (Sub x (rep 2))))
\end{lstlisting}
